% This file is iccc.tex.  It contains the formatting instructions for and acts as a template for submissions to ICCC.  It borrows liberally from the AAAI and IJCAI formats and instructions.  It uses the files iccc.sty, iccc.bst and iccc.bib, the first two of which also borrow liberally from the same sources.


\documentclass[letterpaper]{article}
\usepackage{iccc}


\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\pdfinfo{
/Title (SpaceSheet: Navigating Conceptual Space with a Spreadsheet Interface)
/Subject (Proceedings of ICCC)
/Author (ICCC)}
% The file iccc.sty is the style file for ICCC proceedings.
%
\title{SpaceSheet: Navigating Conceptual Space with a Spreadsheet Interface}
\author{
  Anonymous Author(s)\\
  Anonymous School(s)\\
  \texttt{\{Anonymous Email(s)\}} \\
}
\setcounter{secnumdepth}{0}

\begin{document} 
\maketitle
\begin{abstract}
\begin{quote}
We introduce a new spreadsheet based interface call SpaceSheets for creating novel images and other media. Unlike traditional digital tools, ours is parameterized entirely by a neural network with no preprogrammed rules or knowledge representations. The capability of SpaceSheets to support visual exploration and communication is demonstrated within the context of several domains including facial images, fonts, and english words. SpaceSheets is demonstrated to support the experimentation and exploration of latent spaces enabling more effective design experimentation.
\end{quote}
\end{abstract}

\section{Introduction}

Problem solving can be viewed as a search for a solution within a space. In design, this process involves generating solutions and evaluating their consequences relative to goals and constraints~\cite{simon95}. These experiments are enabled through representations in the form of drawings and diagrams. Computational design tools enable users to construct and manipulate representations digitally. These tools often impose a high cost to design experimentation due to the mismatch between low-level design operations in expressing more abstract design intent.

Generative models learn more compact representations of the training data in a vector space of latent variables. Latent variables are sampled from high-dimensional latent space and can be decoded back into observable values. Additionally, semantic operations can be performed within latent space using vector arithmetic~\cite{white16}.

Spreadsheet interfaces are a ubiquitous part of office productivity suites. They enable users to perform experimental calculations using a set of formulae which define relationships spatially. Automatic recalculation supports experimentation by enabling users to observe the results of their actions immediately and act accordingly


\bibliographystyle{iccc}
\bibliography{iccc,spacesheet}


\end{document}
